### 2023-08-16 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
in each bin by means of the following equation:
\be
\label{eq:statistical_uncertainties}
\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since we discard bins with less than 30 events, the fractional statistical uncertainty
ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
$x$ and $Q^2$ associated to this bin.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$
      for both the neutrino and antineutrinos.
      %
      In addition to the event yield values, we also show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The error bars in the horizontal direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

These statistical uncertainties are displayed in the left panel
of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
to the same event yields as in
Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
now as a function of $x$ after having integrated the event
yields in the range $Q^2 \in [10,100]$ GeV$^2$.
%
The error bar in the vertical direction indicates the statistical uncertainties, while
that in the horizontal direction corresponds to the width of the $x$-bins.
%
Except for the bins with the smallest values of $x$, statistical uncertainties indeed
are at the percent level or smaller for FASER$\nu$2.

In addition to the statistical uncertainties given by Eq.~(\ref{eq:statistical_uncertainties}),
one needs to also estimate the systematic uncertainties associated to the
finite precision in the reconstruction
of the final state leptonic and hadronic variables listed in Table~\ref{tab:FPF_experiments}.
%
For instance, an event which would be classified into a given bin in $(x,Q^2,E_\nu)$ in the case
of a perfect detector may end up being
mis-classified into a different bin in the presence of systematic
shifts associated to the lepton energy $E_\ell$, lepton scattering angle $\theta_\ell$, and
hadronic energy $E_h$, as indicated by  Eq.~(\ref{eq:dis_kinematic_mapping}).

For each source of experimental systematic uncertainty we need to
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
%
Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
From Table~\ref{tab:FPF_experiments} we know that its
acceptance and reconstruction performance are specified by:
\bea
E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
\delta E_\ell \sim 30\% \, 
 \quad \delta E_h \sim 30\% \, ,
 \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
\label{eq:fasernu2systematic_errors}
\eea
To translate the uncertainties in $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
the binned event yields for this reference $\mathcal{D}_0$ sample.

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the absolute difference between the mean number of events in this
bin evaluated for the smeared samples samples and the
central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
\be
\delta_{\rm sys}^{(E_\ell)} N^{(i)} = \Big| \la {N}^{(i)}\ra_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big| \, .
\ee
Systematic errors are treated as uncorrelated among them and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
is straightforward.

Fig.~\ref{fig:percentage_uncertainties_overview}
displays the systematic uncertainties associated
to $E_\ell$, $\theta_\ell$, and $E_h$ variations
for the  measurements
of the double-differential
neutrino scattering cross-section at FASER$\nu$2.
%
The magnitude of each systematic error is plotted as a function
of the average momentum fraction per bin $\la x\ra$
in three different bins of $Q^2$.
%
We indicate separately the results for neutrino and antineutrino projectiles as well as
those associated to inclusive and to charm production measurements.
%
Systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest.
%
The uncertainties associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
between a few percent up to 20\% in the nominal baseline scenario,
and in the case of the latter they are the smallest in the large-$x$ region.
%
Fig.~\ref{fig:error_plot_FASERv2_14} (central and right panels) display
 the integrated event yields for FASER$\nu$2 as a function of $x$ for only
 systematic errors and for the sum in quadrature of statistical and systematic errors.
 %
 For most of the bins, for the baseline performance assumptions the total systematic
 uncertainty is at the $10\%$ and dominates over the statistical uncertainties.

%-----------------------------------------------------------------------
\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
  \caption{\small Estimated systematic uncertainties for the  measurements
    of the double-differential
    neutrino scattering cross-section at FASER$\nu$2.
    %
    We consider the systematic errors
    associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
    and to the hadronic energy $E_h$.
    %
    The size of each source of systematic error is plotted as a function
    of the average momentum fraction per bin $\la x\ra$
    in three different bins of $Q^2$.
    %
    We indicate separately the results for neutrino and antineutrino projectiles as well as
    those associated to inclusive and to charm production measurements.
  }
  \label{fig:percentage_uncertainties_overview}
\end{figure}
%-----------------------------------------------------------------------

The end result of the procedure is the estimate of statistical and systematic uncertainties
for each bin of the measurement, from which a experimental covariance matrix can be constructed as
\be
\label{eq:covmat_definition}
   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
 \ee
  and the same for the associated correlation
 matrix of the measurement
 \be
\label{eq:corrmat_definition}
 \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
 \ee
 The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
 independent of the considered observable and would also apply
 for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.
 %

 Eq.~(\ref{eq:covmat_definition}) assumes that each source of systematic
 uncertainty is 100\% correlated across all the bins of the measurement.
 %
 In the real experiment, the actual covariance matrix will be
 composed by a large number of uncertainty sources, with typical
  HERA and LHC precision measurements characterised by up to hundreds
 of different sources of systematic error.
 %
 In particular, the assumption that a single source of systematic error, say $\delta E_\ell$,
 is fully correlated among all the bins in $(x,Q^2)$ is unlikely to be accurate.
 %
 For this reason, here we neglect bin-by-bin correlations
 and add in quadrature statistical and systematic errors
 \be
\label{eq:covmat_definition_v2}
 {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+ \delta_{ij}\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
\ee
In Eq.~(\ref{eq:covmat_definition_v2}) we have introduced a parameter $f_{\rm red}^{(k)}\le 1$
that gauges the impact of a possible reduction of the $k$-th systematic error
as compared to the default experiment performance.
%
In Sect.~\ref{sec:protonPDFs} we present results for different scenarios
for the systematic uncertainty reduction $f_{\rm red}^{(k)}$.

@@

 In order to generate pseudo-data for double-differential
 LHC neutrino scattering cross-sections, we follow the procedure
 used for the HL-LHC projections of~\cite{AbdulKhalek:2018rok} which was
 also adopted in~\cite{Ethier:2021ydt} and~\cite{Greljo:2021kvv} for SMEFT impact projections
 of vector-boson scattering and high-mass Drell-Yan data at the HL-LHC, respectively.
 %
 The starting point are predictions for inclusive and charm-tagged
 differential neutrino scattering cross-section, denoted generically by
 \be
 \label{eq:theory_dis_projections}
 \mathcal{O}_i^{{\rm (th)}} \equiv \frac{d^2\sigma^{\nu N}(x_i,Q^2_i,y_i)}{dxdy} \, ,\quad
 i=1,\ldots,N_{\rm bin} \, ,
 \ee
 with $(x_i,Q^2_i,y_i)$ labeling the corresponding bin centers.
 %
 The observables $\mathcal{O}_i $ in Eq.~(\ref{eq:theory_dis_projections})
are evaluated with the
{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
to return a fast interpolation grid admitting a generic PDF input,
and with DGLAP evolution effects provided by {\sc\small EKO}~\cite{Candido:2022tld}.
%
PDF evolution and DIS structure functions account for NLO QCD corrections
and target mass effects.
%
No higher-twists corrections are included.
%
Charm structure functions are evaluated in the FONLL general-mass variable-flavour-number
scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} at $\mathcal{O}\lp \alpha_s\rp$
accuracy.
%
For the proton PDF fits we assume a free isoscalar target $N$, while
for the nuclear PDF one we allow for deviations from isoscalarity.

@@

 The central values for the pseudo-data, denoted
 by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
 by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
 by the corresponding statistical and systematic
 uncertainties,
 \begin{equation}
  \label{eq:pseudo_data_v2}
  \mathcal{O}_i^{{\rm (exp)}}
  = \mathcal{O}_i^{{\rm (th)}}
    \left( 1+ r_i \delta_i^{\rm tot}
    \right) \,
    , \qquad i=1,\ldots,N_{\rm bin} \, ,
 \end{equation}
 where the total experimental uncertainty is the sum in quadrature of
 statistical and systematic errors, accounting for a possible reduction
 factor in the latter,
  \be
 \delta_{i}^{\rm tot}
 = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
 \left( f_{\rm red}^{(k)} \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
 \qquad i=1,\ldots,N_{\rm bin} \, ,
 \ee
 and with $r_{i}$ being univariate Gaussian random numbers. 
Similar to the factor $f_{\rm corr}$ in Ref.~\cite{AbdulKhalek:2018rok}, we take the factor $f_{\rm red}$ to be 0.5.
 %
 The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
 together with the corresponding correlations, computed according to Eq.s~\eqref{eq:corrmat_definition}--\eqref{eq:covmat_definition_v2},
%  \be
%\label{eq:covmat_definition_v2}
% {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
% + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
% \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
%\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
%\ee
define then the inputs of the subsequent proton and nuclear PDF determination.

>>>>

The event yields displayed in Fig.~\ref{fig:fasernu2_muon} determine the associated statistical uncertainty 
in each bin,
\be
\label{eq:statistical_uncertainties}
\delta^{\rm (stat)}  N_{\rm ev}^{(i)} = \sqrt{N_{\rm ev}^{(i)}} \, ,
\ee
such that the fractional statistical uncertainty per bin is $\delta^{\rm (stat)}_i=1/\sqrt{N_{\rm ev}^{(i)}}$.
%
Since we discard bins with less than 30 events, the fractional statistical uncertainty
ranges between $\lsim 1\%$ and $\sim 18\%$, depending on the values of
$x$ and $Q^2$ associated to each bin.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
    \centering
    \includegraphics[width = \textwidth]{plots/Event_Rate_FASERv2.pdf}
    \caption{Same as Fig.~\ref{fig:fasernu2_muon} for FASER$\nu$2
      now as a function of $x$ after having integrated the event yields in the range $Q^2 \in [10,100]$ GeV$^2$
      for both the neutrino and antineutrinos.
      %
      In addition to the event yield values, we also show the error bars corresponding to
      statistical errors only (left), systematic errors only (middle), and the
      sum in quadrature of the two (right panel).
      %
      The bars in the horizontal direction indicate the width of the adopted $x$-bins.
      }
    \label{fig:error_plot_FASERv2_14}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The projected statistical uncertainties for muon-neutrino scattering
in the case of FASER$\nu$2 are displayed in the left panel
of Fig.~\ref{fig:error_plot_FASERv2_14}, which corresponds
to the same event yields as in
Fig.~\ref{fig:fasernu2_muon} for 
now as a function of $x$ after having integrated the event
yields in the range $Q^2 \in [10,100]$ GeV$^2$.
%
The error bar in the vertical direction indicates the statistical uncertainties, while
that in the horizontal direction corresponds to the width of the $x$-bins.
%
Except for the bins with the smallest values of $x$, statistical uncertainties indeed
are at the percent level or smaller for this experiment.

In addition to the statistical uncertainties evaluated from Eq.~(\ref{eq:statistical_uncertainties}),
one needs to also estimate the systematic uncertainties associated to the
finite precision in the reconstruction
of the final state leptonic and hadronic variables listed in Table~\ref{tab:FPF_experiments}.
%
For instance, an event which would be classified into a given bin in $(x,Q^2,E_\nu)$ in the case
of a perfect detector may end up being
mis-classified into a different bin in the presence of systematic
shifts associated to the lepton energy $E_\ell$, lepton scattering angle $\theta_\ell$, and
hadronic energy $E_h$, as indicated by  Eq.~(\ref{eq:dis_kinematic_mapping}).

For each independent source of experimental systematic uncertainty, we hence
quantify its impact at the event yield level.
%
In order to determine these bin-by-bin systematic errors,
we extend the calculation delineated in Eq.~(\ref{sec:pseudo-data_generation}) as follows.
%
Let us consider for illustrative purposes the FASER${\nu}$2 detector.
%
From Table~\ref{tab:FPF_experiments} we know that its
acceptance parameters and reconstruction performance are specified by:
\bea
E_\ell \ge 100~{\rm GeV} \, , \quad \theta_\ell \le \tan^{-1}(0.025)\, , \qquad\\
\delta E_\ell \sim 30\% \, 
 \quad \delta E_h \sim 30\% \, ,
 \quad \delta\theta_\ell \sim 0.06~{\rm mrad} \, . 
\label{eq:fasernu2systematic_errors}
\eea
To translate these uncertainties in $\delta E_\ell$, $\delta E_h $,
and $\delta\theta_\ell$ into systematic errors associated to the event yields, 
\be
\label{eq:event_yields_systematic_error}
\delta_{\rm sys}^{(E_\ell)} N_{\rm ev}^{(i)} \, ,\quad
\delta_{\rm sys}^{(E_h)} N_{\rm ev}^{(i)}
\, ,\quad
\delta_{\rm sys}^{(\theta_\ell)} N_{\rm ev}^{(i)} \, ,\qquad i=1,\ldots,N_{\rm bin} \, ,
\ee
we generate first a Monte Carlo set of events, denoted by $\mathcal{D}_0$,
composed by $N_{\rm mc} = 10^7$ samples and determine the assignment of each event
to a point in the $\lp x,Q^2,E_{\nu}\rp$ space.
%
By integrating over this sample by means of Eq.~(\ref{MCintegration}), we determine
the binned event yields for this reference $\mathcal{D}_0$ sample.

We then produce a second Monte Carlo sample $\mathcal{D}_1$ starting from the events
of $\mathcal{D}_0$ which are then smeared with Gaussian distributions whose variances
are given by Eq.~(\ref{eq:fasernu2systematic_errors}).
%
The bin assignment of the events in the smeared sample $\mathcal{D}_1$ will
in general be different from those of the baseline sample.
%
The procedure is repeated $M$ times, leading to
$\mathcal{D}_k$ (with $k=1,\ldots,M$) smeared
samples each one leading to a different binned event yields
$ N_{\rm ev}^{(i)(k)}$.
%
We take the uncertainty associated
to a given systematic source, say $\delta E_\ell$,
to be the absolute difference between the mean number of events in this
bin evaluated for the smeared samples and the
central prediction for the number of events
$ N_{\rm ev}^{(i)}$ as calculated from Eq.~(\ref{MCintegration}):
\be
\delta_{\rm sys}^{(E_\ell)} N^{(i)} = \Big| \la {N}^{(i)}\ra_{E_\ell-{\rm smeared}} -N_{\rm ev}^{(i)}\Big| \, .
\ee
Individual sources of systematic errors are treated as uncorrelated among them and hence
by producing samples where only one source of error is varied at a time
we can determine the systematic errors, Eq.~(\ref{eq:event_yields_systematic_error}), in each bin
for each of the considered experiments.
%
This approach has the benefit that rescaling individual sources of systematic
uncertainties, say to assess the impact of improved detector performance,
becomes straightforward.

Fig.~\ref{fig:percentage_uncertainties_overview}
displays the projected systematic uncertainties associated
to $E_\ell$, $\theta_\ell$, and $E_h$ 
for the  measurements of the double-differential
muon-neutrino scattering  at FASER$\nu$2.
%
The magnitude of each systematic error is plotted as a function
of the average momentum fraction per bin $\la x\ra$
in two different bins of $Q^2$.
%
We indicate separately the results for neutrino and antineutrino projectiles as well as
those associated to inclusive and to charm production measurements.
%
For completeness, we also display in the bottom-right panel the corresponding
statistical uncertainties in the same bins.

%-----------------------------------------------------------------------
\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{plots/percentage_errors.pdf}
  \caption{\small Estimated systematic uncertainties for the  measurements
    of the double-differential
    muon-neutrino scattering cross-section at FASER$\nu$2.
    %
    We consider the systematic errors
    associated to the charged lepton energy $E_\ell$ and scattering angle $\theta_\ell$
    and to the hadronic energy $E_h$.
    %
    The size of each source of systematic error is plotted as a function
    of the average momentum fraction per bin $\la x\ra$
    in two different bins of $Q^2$.
    %
    We indicate separately the results for neutrino and antineutrino projectiles as well as
    those associated to inclusive and to charm production measurements.
    %
    For completeness, we display in the bottom-right panel the corresponding
    statistical uncertainties in the same bins.
  }
  \label{fig:percentage_uncertainties_overview}
\end{figure}
%-----------------------------------------------------------------------

In general, systematic uncertainties associated to the hadronic final state energy $E_h$ appear to be the largest,
reaching up to $\sim 40\%$.
%
We recall that measurement of $E_h$ in addition to the leptonic variables is required to
fix the incoming neutrino energy $E_\nu$, which is different in each event unlike
the case of neutral-current scattering.
%
The uncertainties associated to the charged-lepton energy $E_\ell$ and scattering angle $\theta_\ell$ range
between a few percent up to 20\% in the  baseline scenario listed in Table~\ref{tab:FPF_experiments}.
%
For the $\delta \theta_\ell$ variations, they are smallest in the large-$x$ region
for $x\gsim 0.1$, where they are at the few-percent level typically.
%
Statistical uncertainties are subdominant in most of the bins and are below the 10\% level,
specially at large-$x$ which is the kinematic region benefitting from the largest event rates.

Fig.~\ref{fig:error_plot_FASERv2_14} also displays
 the integrated event yields for FASER$\nu$2 as a function of $x$ for only
 systematic errors and for the sum in quadrature of statistical and systematic errors
 (central and right panels respectively).
 %
 For most of the bins, for the baseline performance assumptions the total systematic
 uncertainty dominates over the statistical uncertainties, with the possible exception
 of the small-$x$ region where statistical and systematic errors are comparable.

The end result of the procedure is an estimate of statistical and systematic uncertainties
for each bin of the measurement, from which a experimental covariance matrix can be constructed as
\be
\label{eq:covmat_definition}
   {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
   + \sum_{k=1}^{n_{\rm sys}}\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp \lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(j)} \rp
   \, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
 \ee
  and the same for the associated correlation
 matrix of the measurement
 \be
\label{eq:corrmat_definition}
 \rho_{ij} =  \frac{{\rm cov}_{ij}}{\sqrt{ {\rm cov}_{ii} }\sqrt{ {\rm cov}_{jj} } } \, . 
 \ee
 The relative covariance matrix, $ {\rm cov}_{ij}/( N_{\rm ev}^{(i)}N_{\rm ev}^{(j)})$, is
 independent of the considered observable and would also apply
 for the double-differential cross-sections Eqns.~(\ref{eq:neutrino_DIS_xsec_FL}) and~(\ref{eq:antineutrino_DIS_xsec_FL}) which are related to the event yields by a constant prefactor.

 The experimental covariance matrix constructed as per
 Eq.~(\ref{eq:covmat_definition}) assumes that each source of systematic
 uncertainty is 100\% correlated across all the bins of the measurement.
 %
 In the real experiment, the actual covariance matrix will be
 composed by a large number of uncertainty sources, with typical
  HERA and LHC precision measurements characterised by up to hundreds
 of different sources of systematic error.
 %
 In particular, the assumption that a single source of systematic error, say $\delta E_\ell$,
 is fully correlated among all the bins in $(x,Q^2)$ is unlikely to be accurate.
 %
 For this reason, following the HL-LHC projection strategy of~\cite{AbdulKhalek:2018rok}
 here we neglect bin-by-bin correlations
 and add in quadrature statistical and systematic errors
 \be
\label{eq:covmat_definition_v2}
 {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)}  N_{\rm ev}^{(i)}\rp^2
+ \lp f_{\rm corr}\rp^2\sum_{k=1}^{n_{\rm sys}} \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} N_{\rm ev}^{(i)} \rp^2
\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, .
\ee
In Eq.~(\ref{eq:covmat_definition_v2}) we have introduced a parameter $f_{\rm red}^{(k)}\le 1$
that gauges the impact of a possible reduction of the $k$-th systematic error
as compared to the default experiment performance.
%
Furthermore, Here $f_{\rm corr}$ represents an effective correction factor that accounts for the fact that data with correlated
systematics may be more constraining than the same data where each source of error is simply
added in quadrature as we do here.
%
A value of $f_{\rm corr}=0.5$, obtained from the inspection of available measurements
 for which the full information
 on correlated systematics is available, was estimated in ~\cite{AbdulKhalek:2018rok}
 and we adopt the same choice here.
%
In Sect.~\ref{sec:protonPDFs} we present results for different scenarios
for the systematic uncertainty reduction $f_{\rm red}^{(k)}$ with respect to the baseline settings.

@@

 In order to generate pseudo-data for double-differential
 LHC neutrino scattering cross-sections, we follow the procedure
 used for the HL-LHC projections of~\cite{AbdulKhalek:2018rok} which was
 also adopted in~\cite{Ethier:2021ydt} and~\cite{Greljo:2021kvv} for SMEFT impact projections
 of vector-boson scattering and high-mass Drell-Yan data at the HL-LHC, respectively.
 %
 The starting point are predictions for inclusive and charm-tagged
 differential neutrino scattering cross-section, denoted generically by
 \be
 \label{eq:theory_dis_projections}
 \mathcal{O}_i^{{\rm (th)}} \equiv \frac{d^2\sigma^{\nu N}(x_i,Q^2_i,y_i)}{dxdy} \, ,\quad
 i=1,\ldots,N_{\rm bin} \, ,
 \ee
 with $(x_i,Q^2_i,y_i)$ labeling the corresponding bin centers.
 %
 The observables $\mathcal{O}_i $ in Eq.~(\ref{eq:theory_dis_projections})
are evaluated with the
{\sc\small YADISM}~\cite{yadism,Candido:2023utz} program
interfaced to {\sc\small PineAPPL}~\cite{Carrazza:2020gss, christopher_schwan_2023_7995675}
to return a fast interpolation grid admitting a generic PDF input,
and with DGLAP evolution effects provided by {\sc\small EKO}~\cite{Candido:2022tld}.
%
PDF evolution and DIS structure functions account for NLO QCD corrections
and target mass effects.
%
No higher-twists corrections are included.
%
Charm structure functions are evaluated in the FONLL general-mass variable-flavour-number
scheme~\cite{Forte:2010ta,Ball:2011mu,Faura:2020oom} at $\mathcal{O}\lp \alpha_s\rp$
accuracy.
%
For the proton PDF fits we assume a free isoscalar target $N$, while
for the nuclear PDF one we allow for deviations from isoscalarity relevant
for a tungsten nucleus.

@@

 The central values for the pseudo-data, denoted
 by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
 by fluctuating the reference theory prediction Eq.~(\ref{eq:theory_dis_projections})
 by the corresponding fractional statistical and systematic
 uncertainties,
 \begin{equation}
  \label{eq:pseudo_data_v2}
  \mathcal{O}_i^{{\rm (exp)}}
  = \mathcal{O}_i^{{\rm (th)}}
    \left( 1+ r_i \delta_i^{\rm tot}
    \right) \,
    , \qquad i=1,\ldots,N_{\rm bin} \, ,
 \end{equation}
 where the total experimental uncertainty is the sum in quadrature of
 statistical and systematic errors, accounting for a possible reduction
 factor in the latter,
  \be
 \delta_{i}^{\rm tot}
 = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
 \left( f_{\rm corr} \times f_{\rm red}^{(k)} \times \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
 \qquad i=1,\ldots,N_{\rm bin} \, ,
 \ee
 and with $r_{i}$ being univariate Gaussian random numbers. 
 %
 As mentioned above, $f_{\rm red}^{(k)}$ is a reduction factor that accounts possible
 improvements in the experimental performance as compared to the baseline
 settings summarised in Sect.~\ref{tab:FPF_experiments}.
 %
 Here we consider two scenarios for the systematic errors: conservative  $f_{\rm red}^{(k)}=1$, so
 no improvement as compared to current projected performance, and  $f_{\rm red}^{(k)}=0.5$, a factor
 two improvement for all relevant sources.
 %
 The pseudo-data generated by means of Eq.~(\ref{eq:pseudo_data_v2}),
 together with the corresponding correlations, computed according to Eq.s~\eqref{eq:corrmat_definition}--\eqref{eq:covmat_definition_v2},
%  \be
%\label{eq:covmat_definition_v2}
% {\rm cov}_{ij} = \delta_{ij} \lp \delta^{\rm (stat)} \mathcal{O}_i^{\rm (th)} \rp^2
% + \delta_{ij}\sum_{k=1}^{n_{\rm sys}}
% \lp f_{\rm red}^{(k)}\rp^2\lp \delta_{\rm sys}^{(k)} \mathcal{O}_i^{\rm (th)} \rp^2
%\, ,\qquad i,j=1,\ldots,N_{\rm bin} \, ,
%\ee
define then the inputs of the subsequent proton and nuclear PDF determination.
